Modelling last glacial cycle ice dynamics in the Alps

### 2017-01-23 articles/cycle/alps-cycle.tex
Rework outline and fig. list after disc. Matthias.

\section{Main}
\subsection{Introduction}
\subsection{Ice cap evolution}
    Fig.~\ref{fig:lgmvel} -- Snapshot at 21\,ka and volume time series.
\subsection{Timing of the LGM}
    Fig.~\ref{fig:timing} -- Timing of the LGM and area time series.
\subsection{Ice thickness}
    Fig.~\ref{fig:trimlines} -- Ice thickness comparison to trimlines.
\subsection{Erosion potential}
    Fig.~\ref{fig:erosion} -- Integrated erosion potential.

\section{Methods}
\subsection{Overview}
    Tab. -- Model parameters
\subsection{Ice rheology}
\subsection{Basal sliding}
\subsection{Bedrock deformation}
\subsection{Surface mass balance}
\subsection{Climate forcing}
    Fig.~\ref{fig:inputs} -- Climate and geothermal model inputs.\\
    Tab. -- Records\\
    Fig.~\ref{fig:timeseries} -- Low-resolution time series.\\
    Fig.~\ref{fig:footprints} -- Low-resolution ice cover.

@@

    \begin{figure}
      \centerline{\includegraphics{alpcyc_hr_trimlines}}
      \caption{Ice thickness comparison to trimlines.}
      \label{fig:trimlines}
    \end{figure}

>>>>

\section{Main}
\subsection{Introduction}
\subsection{Glacier dynamics}
    Fig.~\ref{fig:lgmvel} -- Snapshot at 21\,ka and volume time series.\\
    Fig.~\ref{fig:timing} -- Timing of the LGM and area time series.\\
    Fig.~\ref{fig:profiles} -- Individual glacier extent profiles.
\subsection{Erosion potential}
    Fig.~\ref{fig:erosion} -- Integrated erosion potential.

\section{Methods}
\subsection{Ice sheet model set-up}
    Tab. -- Model parameters\\
    Fig.~\ref{fig:inputs} -- Climate and geothermal model inputs.\\
\subsection{Palaeo-climate forcing}
    Tab. -- Records\\
    Fig.~\ref{fig:timeseries} -- Low-resolution time series.\\
    Fig.~\ref{fig:footprints} -- Low-resolution ice cover.

@@

    \begin{figure}
      \centerline{\includegraphics{alpcyc_hr_profiles}}
      \caption{Individual glacier extent profiles.}
      \label{fig:profiles}
    \end{figure}
